
% Manual creation of bibliography (as opposed to automatic BibTeX creation).
% https://www.overleaf.com/learn/latex/hyperlinks
% https://web.iit.edu/sites/web/files/departments/academic-affairs/graduate-academic-affairs/pdfs/biblio-help2.pdf
% \begin{thebibliography}{largest number of items as integer}
\begin{thebibliography}{2}

\bibitem[Bartels 1995]{Bartels-1995} Bartels RH, Beatty JC, Barsky BA. An introduction to splines for use in computer graphics and geometric modeling. Morgan Kaufmann; 1995 Sep 15.

\bibitem[Cottrell 2009]{Cottrell-2009} Cottrell JA, Hughes TJ, Bazilevs Y. Isogeometric analysis: toward integration of CAD and FEA. John Wiley \& Sons; 2009 Aug 11.

\bibitem[Heinrich 2016]{Heinrich-2016} Heinrich G.  Image segementation using DIGITS 5, NVIDIA Developer Blog.  \url{https://devblogs.nvidia.com/image-segmentation-using-digits-5}; 2016 Nov 10.

\bibitem[IRCAD 2019]{IRCAD-2019}IRCAD France.  3D-IRCADb 01 database, 3D CT-scans of 10 women and 10 men. \url{https://www.ircad.fr/research/3d-ircadb-01/}; accessed 2019 Aug 29.

\bibitem[Piegl 2012]{Piegl-2012} Piegl L, Tiller W. The NURBS book: edition 2. Springer Science \& Business Media; 2012 Dec 6.

\bibitem[Rogers 2000]{Rogers-2000} Rogers DF. An introduction to NURBS: with historical perspective. Elsevier; 2000 Aug 22.

\bibitem[Ronneberger 2015]{Ronneberger-2015} Ronneberger O, Fischer P, Brox T. U-net: Convolutional networks for biomedical image segmentation. In International Conference on Medical image computing and computer-assisted intervention. \url{https://arxiv.org/abs/1505.04597}; 2015 Oct 5 (pp. 234-241). Springer, Cham.

\bibitem[Shiach 2015]{Shiach-2015} Shiach J. B\'ezier Curves.  Mathematics of Computer Graphics and Virtual Environments.  \url{https://youtu.be/2HvH9cmHbG4}; 2015 Mar 09.

\bibitem[Shiach 2015b]{Shiach-2015b} Shiach J. B-Splines.  Mathematics of Computer Graphics and Virtual Environments.  \url{https://youtu.be/qhQrRCJ-mVg}; 2015 Mar 13.

\end{thebibliography}

